To be FAIR: Theory Specification Needs an Update

### 2025-02-19 manuscript.Rmd
rephrase paradigm section

Successful communication requires shared background knowledge between sender and receiver [@vogtFAIR20Extending2024].
The notion of "normal science" describes a phase in which a scientific community operates within the context of a shared paradigm,
creating the background knowledge needed for mutual understanding and productive scientific work [@kuhnStructureScientificRevolutions2009].
In reality, however, paradigms are rarely clear-cut, and shared background knowledge can come from different sources, or be problematically absent.
From a pragmatic perspective,
this underscores the importance of being as explicit as possible about assumptions and ontological definitions when making theory Accessible,
while acknowledging that Accessibility exists on a spectrum, 
and that it is impossible to eliminate all ambiguity.
Rather, it may benefit scientific discourse to anticipate misunderstanding,
and use it to drive further explication of theory.
In sum, efforts to communicate theory clearly, with as few dependencies on shared background knowledge as possible, including by formalization, explication of assumptions,
and cross-references to resources that provide relevant context (papers, ontologies, macro-theories, theories of measurement)
will advance its Accessibility [@langeChecklist2025].

>>>>

Successful communication requires shared background knowledge between sender and receiver [@vogtFAIR20Extending2024].
The notion of "normal science" describes a phase in which a scientific community operates within the context of a shared paradigm,
creating the background knowledge needed for mutual understanding and productive scientific work [@kuhnStructureScientificRevolutions2009].
In reality, however, paradigms are rarely clear-cut, and shared background knowledge can come from different sources,
including education, cultures of communication, and availability of particular instruments for observation, measurement, and analysis - or it can be problematically absent.
From a pragmatic perspective,
this underscores the importance of being as explicit as possible about assumptions and ontological definitions when making theory Accessible,
while acknowledging that Accessibility exists on a spectrum, 
and that it is impossible to eliminate all ambiguity.
Rather, it may benefit scientific discourse to anticipate misunderstanding,
and use it to drive further explication of theory.
In sum, efforts to communicate theory clearly, with as few dependencies on shared background knowledge as possible, including by formalization, explication of assumptions,
and cross-references to resources that provide relevant context (papers, ontologies, macro-theories, theories of measurement)
will advance its Accessibility [@langeChecklist2025].
